### 2013-11-06 inst/examples/policycosts/errors_table.Rmd
updated writeup with tweaks to figures

```{r}
#df <- df[1:5]
library(xtable)
print(xtable(df), type="html")
writeLines(print(xtable(df)), "output.md")
system("pandoc output.md -o output.pdf")
```

>>>>

```{r results="asis"}
#df <- df[1:5]
library(xtable)
print(xtable(df), type="html")
writeLines(print(xtable(df)), "output.md")
system("pandoc output.md -o output.pdf")
write.csv(df, "output.csv")
```
